---
title: "Data Modification"
author: "Roghan"
date: "5 April 2023"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(GGally)
library(ggplot2)
```

***Read Data

```{r}
df <- read.csv("./preprocess.csv")
df %>% head
```

***Data modification for model creation

```{r}
head(df)
```

```{r}
lab= c("1-3 ","3-6","6-9","9-12","12+")
val= c(0,1,2,3,4)


for (x in 1:length(lab)){
  df$btime[df$btime==lab[x]]<-val[x]
  df$atime[df$atime==lab[x]]<-val[x]
}

df
```
```{r}
cols= colnames(df)[8:19]
cols
```
```{r}
i=1
c=1

newcols= c("time", "devstudy", "conc", "bed", "affbed", "tire")

while(i!=13){
  final= c()
  
  for (row in 1:nrow(df)) {
    v1 <- as.numeric(df[row, cols[i]])
    v2 <- as.numeric(df[row, cols[i+1]])
    
    if (i==7){
      final= append(final, v1-v2)
    }
    else{
      final= append(final, v2-v1)
    }
  }

  i= i+2
  df[,newcols[c]] <- final
  c= c+1
}
```
```{r}
df
```
```{r}
for(x in colnames(df)[8:ncol(df)]){
  df[,x]= as.numeric(df[,x])
}

```

```{r}
newdf= data.frame(devuse.score= df$time + df$devstudy + df$conc)
newdf= cbind(newdf, sleep.score= df$bed + df$affbed + df$tire)
newdf= cbind(newdf, social.score= df$socdist + df$isolate + df$personality + df$lazy)
newdf= cbind(newdf, psych.score= df$boredom + df$psycho + df$afford + df$unhealthy + df$covidstress)
newdf= cbind(newdf, acad.score= df$devicegpa + df$assgn + df$f2f + df$quiz)

```
```{r}
newdf
```
1. devuse.score: 
      Higher the score -> More usage time, Negatively affected health
      Lower the score -> Lesser usage time, Positive/No affect in health

2. sleep.score:
      Higher the score -> Lesser sleep time, Negatively affected health
      Lower the score -> Relatively More sleep time, Positive/No affect in health

3. social.score:
      Higher the score -> Lesser interaction with people, Negatively affected social health
      Lower the score -> Relatively More interaction with other people, Positive/No affect in social health

4. psych.score:
      Higher the score -> Students psychologically affected, Negatively affects psych health
      Lower the score -> Relatively less psychologically affected, Positively/No affects psych health 

5. acad.score:
      Higher the score -> Student not interested to study, Negatively affected grades
      Lower the score -> Student relatively more inclined to study, Positive/No affect in grades

```{r}
ggpairs(newdf)
```

```{r}
write.csv(newdf, "C:/Users/rogha/OneDrive/Documents/MS WORD FILES/EDA/Project/Review-2/parameters.csv", row.names=FALSE)
```

