---
title: "K-Means Clustering"
author: "Roghan"
date: "5 April 2023"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(GGally)
library(ggplot2)
```

***Read Data

```{r}
df <- read.csv("./preprocess.csv")
df %>% head
```

```{r}
newdf <- read.csv("./parameters.csv")
newdf %>% head
```

```{r}
library(factoextra)
library(ggfortify)
```

```{r}
clustering= data.frame(cgpa= df$cgpa)
names= c("c1","c2", "c3", "c4", "c5")

for (i in c(1:5)){
  kmean2 <- kmeans(newdf, i)
  clustering[,names[i]]= kmean2$cluster
}
```

```{r}
clustering
```

```{r}
clustering %>%
  ggplot(aes(x=cgpa, fill=as.character(c3))) +
  geom_bar(position="dodge") +
  theme_bw()
```
Clustering by 3, gives us a clear idea as to how the academic performance varies according to cluster.

```{r}
prcomp(newdf)
```

```{r}
kmean <- kmeans(newdf, 3)
kmean$centers
```
```{r}
store$class= kmean$cluster
```


```{r}
autoplot(kmean, newdf, frame = TRUE)
```
Cluster-1: Positively Impact in Health and Positively impacts Academics
Cluster-2: Negatively Impact in Health and Neutral impact Academics
Cluster-3: Neutral Impact in Health and Negatively impacts Academics

***Adding class label to main dataframe

```{r}
df= df[, c(1:7)]
df
```
```{r}
df= cbind(df, newdf)
```

```{r}
df$class= kmean$cluster
```
```{r}
df= df[, c(2:ncol(df))]
df
```

***Encoding

```{r}
lab= c("Female","Male")
val= c(0,1)


for (x in 1:length(lab)){
  df$sex[df$sex==lab[x]]<-val[x]
}

lab= c("First/Freshman","Second/ Sophomore", "Third/Junior", "Fourth/Senior", "Other")
val= c(0,1,2,3,4)


for (x in 1:length(lab)){
  df$yr[df$yr==lab[x]]<-val[x]
}

lab= c("18-24","25-30", "+30")
val= c(0,1,2)


for (x in 1:length(lab)){
  df$age[df$age==lab[x]]<-val[x]
}

lab= c("60-69","70-79", "80-89", "+90")
val= c(0,1,2,3)


for (x in 1:length(lab)){
  df$cgpa[df$cgpa==lab[x]]<-val[x]
}

lab= c("Laptop", "Mobile phone", "I pad/ Tablet", "Personal Computer", "Other")
val= c(0,1,2,3,4)


for (x in 1:length(lab)){
  df$bdevice[df$bdevice==lab[x]]<-val[x]
  df$adevice[df$adevice==lab[x]]<-val[x]
}


df
```

```{r}
write.csv(df, "C:/Users/rogha/OneDrive/Documents/MS WORD FILES/EDA/Project/Review-2/kmeans.csv", row.names=FALSE)
```
